Reducing iptables configuration complexity using chains

### 2014-04-20 iptables/presentation.tex
improve sentence
add overview
use Tutorial example as description
add remark about order of the rules

@@

    The last rule matches everything, so if a packet didn't match a previous rule, it will be rejected.

@@

    \frametitle{Realworld example : setup}

@@

    \frametitle{Realworld example : webserver}

@@

    \frametitle{Realworld example : sysadmin PCs}

@@

    \frametitle{Realworld example : webmaster PCs}

@@

    \frametitle{Realworld example : access to SMB}

@@

    \textbf{Warning :} check conditions of chain ending

>>>>

    \frametitle{Overview}
      \item introduction to iptables
      \item optimizing configuration with an example setup

@@

    The last rule matches everything, so if a packet didn't match a previous rule, it will be rejected.\\
    \textbf{Remark:} the order of the rules is important

@@

    \frametitle{Tutorial example : setup}

@@

    \frametitle{Tutorial example : webserver}

@@

    \frametitle{Tutorial example : sysadmin PCs}

@@

    \frametitle{Tutorial example : webmaster PCs}

@@

    \frametitle{Tutorial example : access to SMB}

@@

    \textbf{Warning :} check conditions of ending chains
